Modelling the emergence of whisker barrels

### 2020-06-17 paper/briefpaper/brief.tex
Adds a caption for Fig 3, the sensitivity analysis

% Some document-defined commands
\newcommand*\dif{\mathop{}\!\mathrm{d}}
\newcommand{\cmnt}[1]{\textcolor{blue}{#1}}
\newcommand{\stu}[1]{\textcolor{red}{#1}}
\newcommand{\dvrg}{\nabla\vcdot\nabla}
\newcommand{\e}{\emph}
\newcommand{\bol}{\textbf}
\newcommand{\mb}[1]{\mathbf{#1}}
\makeatletter
\newcommand*\vcdot{\mathpalette\vcdot@{.35}}
\newcommand*\vcdot@[2]{\mathbin{\vcenter{\hbox{\scalebox{#2}{$\m@th#1\bullet$}}}}}
\newcommand{\code}[1]{\textsf{#1}}
% Nice norms:
\usepackage{mathtools}
\DeclarePairedDelimiter{\norm}{\lVert}{\rVert}

@@

% Full page width
\begin{figure}
  \begin{fullwidth}
    \includegraphics[width=\linewidth]{./Fig3.png}
    \caption{\cmnt{Sensitivity analysis. Column \textbf{A} shows...}}
    \label{fig:sens}
  \end{fullwidth}
\end{figure}

@@

% Quick check that noise free result is within 1 SD for the noisier initial conditions
%         Noisefree    Normal noise    NF SD from Normal?   Noisy            NF SD from Noisy?
% delta   0.0928       0.089(0.004)    <1                   0.090 (0.005)    <1
% eta     114.31       113.5(1.2)      <1                   115 (1.9)        <1
% omega   0.21649      0.2165(0.0001)  <1                   0.2166 (0.0003)  <1

>>>>

% Some document-defined commands
\newcommand*\dif{\mathop{}\!\mathrm{d}}
\newcommand{\cmnt}[1]{\textcolor{blue}{#1}}
\newcommand{\stu}[1]{\textcolor{red}{#1}}
\newcommand{\dvrg}{\nabla\vcdot\nabla}
\newcommand{\e}{\emph}
\newcommand{\bol}{\textbf}
\newcommand{\mb}[1]{\mathbf{#1}}
\makeatletter
\newcommand*\vcdot{\mathpalette\vcdot@{.35}}
\newcommand*\vcdot@[2]{\mathbin{\vcenter{\hbox{\scalebox{#2}{$\m@th#1\bullet$}}}}}
\newcommand{\code}[1]{\textsf{#1}}
% Nice norms:
\usepackage{mathtools}
\DeclarePairedDelimiter{\norm}{\lVert}{\rVert}
% Degrees symbol:
\usepackage{textcomp}

@@

% Full page width
\begin{figure}
  \begin{fullwidth}
    \includegraphics[width=\linewidth]{./Fig3.png}
    \caption{
      \cmnt{\textbf{A} Sensitivity of the system pattern
        metrics $\delta(t)$ (top row), $\omega(t)$ (middle row) and $\eta(t)$
        (bottom row), evaluated at $t=30000$ steps,
        to three classes of perturbation. $y$-axes and colour scales have identical ranges
        to the colour scales in Fig.\,\ref{fig:paramsweep}, to ease comparison
        with the parameter exploration.
        %
        \emph{Column 1:} Random noise drawn from a uniform distribution,
        $(\gamma_{max}-\gamma_{min})\,U(0,\nu_\gamma)$, added
        to the values for the interaction parameters, $\gamma_{i,j}$ used in
        Fig.\,\ref{fig:main}.
        %
        \emph{Column 2:} Random noise $(\rho_{max} - \rho_{min})\,U(0, \nu_{\rho})$
        was added to each hex element of $\rho_1(\mb{x})$ and $\rho_2(\mb{x})$ and the result
        was smoothed by convolution with a symmetric 2D
        Gaussian kernel of width $\sigma_\rho$. Colour maps in this column
        thus show the effect of changing the magnitude and the length scale of
        noise in the guidance fields.
        %
        \emph{Column 3:} Colour maps show the result of setting the rotational angle
        of the linearly varying guidance field, $\rho_1(\mb{x})$, to $\phi_{\rho_1}$,
        and modifying its overall gain to $G_{\rho_1}$, whilst keeping the
        parameters of $\rho_2(\mb{x})$
        unchanged from those used in the simulation in
        Fig.\,\ref{fig:main}, for which $\phi_{\rho_1}=6$\textdegree~and
        $\phi_{\rho_2}=84$\textdegree.
        %
        \textbf{B} Four ways in which the perturbations in \textbf{A} affect
        the patterns. i) The effect of significant interaction parameter noise
        causes barrels to become swapped from the positions they would
        otherwise take. ii) High magnitude, short lengthscale noise in
        $\rho(\mb{x})$ leads to `wiggly' boundaries between barrels. iii)
        Shows the effect of reducing the slope of $\rho_1$ (by a factor of 10)
        which reduces the strength of the axons' interaction with the guidance
        field in the left-right sense. Barrel rows B, C and D become `crushed'
        down the center line, and edge barrels dominate. iv) The effect of
        rotating $\rho_1$ by 20\textdegree~is a relatively mild distortion of
        the pattern in the anticlockwise sense.
      }
    }
    \label{fig:sens}
  \end{fullwidth}
\end{figure}

@@

% Quick check that noise free result is within 1 SD for the noisier initial conditions
%         Noisefree    Normal noise    NF SD from Normal?   Noisy            NF SD from Noisy?
% delta   0.0928       0.089(0.004)    <1                   0.090 (0.005)    <1
% eta     0.2124       0.2108(0.002)   <1                   0.2136 (0.004)   <1
% omega   0.21649      0.2165(0.0001)  <1                   0.2166 (0.0003)  <1
